---
title: "P8105 HW6"
author: "Yuchen Zheng"
date: "12/1/2021"
output: github_document
---

```{r}
library(tidyverse)
library(readr)
library(modelr)
```

## Problem 1

Load and clean data
```{r}
bw_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(babysex = factor(babysex),
         frace = factor(frace),
         malform = factor(malform),
         mrace = factor(mrace)) 

bw_df %>% skimr::skim()
```

I want to see if there is a relationship between mother's pre-pregnancy weight and baby's birth weight and mother's weight gain during pregnancy and baby's birth weight by plotting scatterplots.
```{r}
bw_df %>% 
  select(bwt,wtgain, ppwt) %>% 
  pairs()

bw_df %>% 
  ggplot(aes(x = wtgain, y = bwt)) +
  geom_point()

bw_df %>% 
  ggplot(aes(x = ppwt, y = bwt)) +
  geom_point()

bw_df %>% 
  ggplot(aes(x = delwt, y = bwt)) +
  geom_point()

bw_df %>% 
  ggplot(aes(x = mheight, y = bwt)) +
  geom_point()
```

fit a model using mother's pre-pregnancy weight and mother's weight gain during pregnancy
```{r}
fit1 = lm(bwt ~ ppwt + wtgain + mheight, data  = bw_df)

fit1 %>% broom::tidy()

```

```{r}
bw_df %>% 
  modelr::add_residuals(fit1) %>% 
  ggplot(aes(x = resid)) +
  geom_density() 
```

fit a model using length at birth and gestational age as predictors
```{r}
fit2 = lm(bwt ~ blength + gaweeks, data = bw_df)

fit2 %>% broom::tidy()

bw_df %>% 
  modelr::add_residuals(fit2) %>% 
  ggplot(aes(x = resid)) +
  geom_density() 
```

fit a model using head circumference, length, sex and all interactions
```{r}
fit3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bw_df)

fit3 %>% broom::tidy()

bw_df %>% 
  modelr::add_residuals(fit3) %>% 
  ggplot(aes(x = resid)) +
  geom_density() 
```

```{r}
cv_df = 
  crossv_mc(bw_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_fit_df=
  cv_df %>% 
  mutate(
    fit1 = map(.x = train, ~lm(bwt ~ ppwt + wtgain + mheight, data  = .x)),
    fit2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_fit1 = map2_dbl(.x = fit1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_fit2 = map2_dbl(.x = fit2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_fit3 = map2_dbl(.x = fit3, .y = test, ~rmse(model = .x, data = .y)),
  )

cv_fit_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

## Problem 2

