---
title: "P8105 HW6"
author: "Yuchen Zheng"
date: "12/1/2021"
output: github_document
---

```{r}
library(tidyverse)
library(readr)
library(modelr)
```

## Problem 1

Load and clean data
```{r}
bw_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(babysex = factor(babysex),
         frace = factor(frace),
         malform = factor(malform),
         mrace = factor(mrace)) 

bw_df %>% skimr::skim()
```

I want to see if there is a relationship between mother's pre-pregnancy weight and baby's birth weight and mother's weight gain during pregnancy and baby's birth weight by plotting scatterplots.
```{r}
bw_df %>% 
  select(bwt,wtgain, ppwt) %>% 
  pairs()

bw_df %>% 
  ggplot(aes(x = wtgain, y = bwt)) +
  geom_point()

bw_df %>% 
  ggplot(aes(x = ppwt, y = bwt)) +
  geom_point()

bw_df %>% 
  ggplot(aes(x = delwt, y = bwt)) +
  geom_point()

bw_df %>% 
  ggplot(aes(x = mheight, y = bwt)) +
  geom_point()
```

fit a model using mother's pre-pregnancy weight and mother's weight gain during pregnancy
```{r}
fit1 = lm(bwt ~ ppwt + wtgain + mheight, data  = bw_df)

fit1 %>% broom::tidy()

```

```{r}
bw_df %>% 
  add_residuals(fit1) %>% 
  add_predictions(fit1) %>%  
  ggplot(aes(x = pred, y = resid)) +
  geom_point() 
```

fit a model using length at birth and gestational age as predictors
```{r}
fit2 = lm(bwt ~ blength + gaweeks, data = bw_df)

fit2 %>% broom::tidy()

bw_df %>% 
  modelr::add_residuals(fit2) %>% 
  ggplot(aes(x = resid)) +
  geom_density() 
```

fit a model using head circumference, length, sex and all interactions
```{r}
fit3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bw_df)

fit3 %>% broom::tidy()

bw_df %>% 
  modelr::add_residuals(fit3) %>% 
  ggplot(aes(x = resid)) +
  geom_density() 
```

```{r}
cv_df = 
  crossv_mc(bw_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_fit_df=
  cv_df %>% 
  mutate(
    fit1 = map(.x = train, ~lm(bwt ~ ppwt + wtgain + mheight, data  = .x)),
    fit2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_fit1 = map2_dbl(.x = fit1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_fit2 = map2_dbl(.x = fit2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_fit3 = map2_dbl(.x = fit3, .y = test, ~rmse(model = .x, data = .y)),
  )

cv_fit_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_bootstrap_results = 
  weather_df %>% 
  select(tmax, tmin) %>% 
  bootstrap(n = 5000, id = "strap_number") %>%  #draw 10 samples with replacement have the same size as the filtered dataset
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results_coeff = map(models, broom::tidy),
    results_rsquare = map(models, broom::glance)
  ) %>% 
  select(strap_number, results_coeff, results_rsquare) %>% 
  unnest(results_coeff) %>% 
  select(strap_number,term, estimate, std.error, results_rsquare) %>% 
  unnest(results_rsquare) %>% 
  select(strap_number, term, estimate, std.error, adj.r.squared)

```

```{r}
beta0_df = 
  weather_bootstrap_results %>% 
  filter(term == "(Intercept)") %>% 
  mutate(term = "beta0") %>%
  select(strap_number, term, estimate, std.error)

beta0_df %>% 
  ggplot(aes(estimate)) +
  geom_density()

beta0_bar = mean(beta0_df$estimate)
std = sd(beta0_df$estimate)
cbind(CIlower = beta0_bar - 1.96 * 5 / 10, CIupper = beta0_bar + 1.96 * 5 / 10)
```

```{r}
beta1_df = 
  weather_bootstrap_results %>% 
  filter(term == "tmin") %>% 
  mutate(term = "beta1") %>% 
  select(strap_number, term, estimate)

beta1_df %>% 
  ggplot(aes(estimate)) +
  geom_density()


```

```{r}
adj_rsquare_df = 
  weather_bootstrap_results %>% 
  select(strap_number, adj.r.squared) %>% 
  distinct(strap_number, .keep_all = TRUE)

adj_rsquare_df %>% 
  ggplot(aes(adj.r.squared)) +
  geom_density()
```

```{r}
fit_weather = lm(tmax ~ tmin, data = weather_df)

summary(fit_weather)

fit_weather %>% broom::glance()
fit_weather %>% broom::tidy()
```

